\documentclass[11pt,a4paper,sans]{moderncv} 
\moderncvstyle{banking}   
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}     
\usepackage{url}
\usepackage{textcomp}
% adjust the page margins
\usepackage[scale=0.75]{geometry}

\usepackage{import}

\name{Yuanyuan}{Xu}

\address{Wuxi, Jiangsu, China}

\phone[mobile]{+86 15600159007}

\email{xuyuanyuan102888@outlook.com}  

\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\small{I have over 6 years of working experience in both AI application, data science and Python developer, which shows excellent performance and teamwork ability. I am a quick learner and I want to explore data patterns that can drive meaningful results for the business.}


\section{Experience}

\vspace{5pt}

\begin{itemize}
\item{\cventry{}{\textbf{Data Scientist \& AI Engineer}}{Bekaert - Global Advanced Digital Solution}{2023 Jan\textasciitilde{}now Remote}{}{}}
\begin{itemize}
\textbf{Project 1: Industrial Process Optimization (MLOps)}

- Migrated archived SAS repositories to Python ML models with PySpark ETL processing.

- Transformed manufacturing data using Azure Synapse and PySpark for real-time analytics.

- Designed and developed Machine Learning models for real-time prediction.

\textbf{Business Impact:} Cost saving 1.5M€ per plant per year, with actual payback rate 1.9.

\textbf{Technical Stack:} Azure Synapse, Python, PySpark, SAS CLI, PowerBI, Azure DevOps
\vspace{10pt}

\textbf{Project 2: Sentiment Analysis (AI Application)}

- Built pipeline to extract financial metrics and forward-looking business strategy statements.

- Implemented RAG system with GPT-4o for sentiment scoring.

- Created regularization algorithms for sentiment score smoothing and validation.

\textbf{Business Impact:} Deliver quantitative analysis to predict customer demand across sale teams.

\textbf{Technical Stack:} Prompt Engineering, RAG, Financial Analytics
\vspace{10pt}

\textbf{Project 3: Patent Landscaping (AI Application)}

- Developed GenAI bot system with LangChain for automated patent analysis and categorization.

- Implemented GPT-4, Gemini, and AutoGen integration for intelligent patent processing.

- Built keyword clustering and priority assessment algorithms for landscape analysis.

\textbf{Business Impact:} Streamlined patent analysis workflow and save labor examining time.

\textbf{Technical Stack:} Prompt Engineering, AutoGen, LangChain
\vspace{10pt}

\end{itemize}

\item{\cventry{}{\textbf{Data Engineer \& Data Analyst}}{Bekaert Technology Research Development Company}{2020 Jan \textasciitilde{}2022 Dec Wuxi}{}{}}
\begin{itemize}
\textbf{Project 1: Portfolio Analysis (Business Analytics / MLOps)}

- Built comprehensive ETL pipeline using Azure Synapse Analytics for portfolio data processing.

- Developed SQL-based data warehouse with interactive PowerBI dashboards for business insights.

- Created KPI metrics and performance analytics for investment decision support.

\textbf{Business Impact:} Enabled data-driven investment decisions and portfolio optimization for sales team.

\textbf{Technical Stack:} Azure Synapse Analytics, SQL, PowerBI, Data Warehousing
\vspace{10pt}

\textbf{Project 2: Tensile Strength Predictive Model (MLOps)}

- Developed time-series forecasting model using Scikit-learn for manufacturing quality prediction.

- Built model evaluation dashboard with cross-validation and performance metrics.

- Deployed FastAPI service with Azure DevOps for real-time predictions.

\textbf{Business Impact:} Cost saving 1.8M¥ per year with actual payback rate 0.6. 

\textbf{Technical Stack:} Python, Pandas, Scikit-learn, Plotly, FastAPI, Azure DevOps
\vspace{20pt}


\\

\textbf{Project 3: Die Driver Hypothesis Test \& Predictive Model (MLOps)}

- Built predictive ML model with hypothesis testing for manufacturing optimization.

- Implemented data preprocessing pipeline with feature engineering and quality metrics.

- Developed Plotly dashboards for performance visualization and manufacturing insights.

- Created FastAPI service with Azure DevOps deployment for production integration.

\textbf{Business Impact:} Cost saving 3.8M¥ per year with actual payback rate 1.2.   

\textbf{Technical Stack:} Python, Pandas, Scikit-learn, Plotly, FastAPI, Azure DevOps
\vspace{10pt}

\textbf{Project 4: Vehicle Trajectory Tracking (Data Analytics)}

- Processed GPS trajectory data with Pandas and coordinate transformation algorithms.

- Built trajectory analysis engine with distance calculations and acceleration analysis.

- Developed FastAPI service with Plotly visualizations for real-time tracking dashboards.

- Implemented RDP algorithm for trajectory optimization and multi-track processing.

\textbf{Technical Stack:} Python, Pandas, Plotly, FastAPI, Azure DevOps, GPS Data Processing
\vspace{10pt}

\end{itemize}

\item{\cventry{}{\textbf{Python Developer}}{Bekaert Technology Research Development Company}{2019 Sep \textasciitilde{}2020 Dec Wuxi}{}{}}
\begin{itemize}
\textbf{Project 1: Industrial IoT \& Manufacturing Optimization (Computer Vision)}

- Developed Python/OpenCV backend pipeline for real-time magnetic point detection and monitoring.

- Implemented FastAPI REST services for data collection and process optimization.

- Built computer vision algorithms for automated quality control in manufacturing processes.

- Implemented real-time data processing with Azure Stream Analytics for production monitoring.

- Built FastAPI service with 20-minute batch processing for predictive maintenance.

- Architected IoT solution connecting IR thermometers and PLCs via Azure IoT Hub.

\textbf{Business Impact:} Cost saving 463k€ per plant during 2023 to 2024 with actual payback rate 0.9.

\textbf{Technical Stack:} Azure Synapse Analytics, Python, OpenCV, FastAPI, Computer Vision Algorithms
\vspace{10pt}

\textbf{Project 2: Web Calculator (Web Applications \& Cloud Infrastructure)}

- Developed React/FastAPI web app serving 200+ users across different time zones, featuring dynamic form builder with Dash components for custom quote modeling, authentication with hierarchical roles (Admin/Sales/Developer), and multi-currency engine with auto-rate fetching.

- Architected hybrid storage: SQLite for transactional data, Azure Blob for contract PDFs.

- Implemented CI/CD via Azure Pipelines (Docker > Azure WebApp) with zero-downtime deployments.

\textbf{Business Impact:} Enabled 10M+ quarterly deals across different regions.

\textbf{Technical Stack:} FastAPI, React, Docker, Azure Web Apps, SQLite, Azure Blob Storage
\vspace{10pt}

\textbf{Project 3: Calculate Internal Lamellar Spacing (Computer Vision)}

- Converted MATLAB scripts to Python-based end-to-end image processing pipeline.

- Developed automated microstructure analysis for material science applications.

- Implemented OpenCV algorithms for precise lamellar spacing measurements.

\textbf{Business Impact:} Estimate cost saving 170k€ per year.

\textbf{Technical Stack:} MATLAB, Python, OpenCV, Image Processing
\vspace{10pt}

\textbf{Project 4: Micro Structure (Data Analytics / Machine Learning)}

- Built comprehensive backend pipeline for microstructure image classification and analysis.

- Implemented data extraction, cleaning, and feature engineering for material characterization.

- Developed machine learning models for automated microstructure classification.

\textbf{Business Impact:} Estimate cost saving 82k€ per year.

\textbf{Technical Stack:} Python, Scikit-learn, OpenCV, Data Analytics
\vspace{10pt}

\end{itemize}

\end{itemize}
\section{Internship}

\vspace{5pt}
\item{\cventry{Apr 2018--Oct 2018}{\textbf{Parameter Study of Blade-Disc Attachment (Thesis Internship)}}{Siemens Industrial Turbomachinery AB}{Finspång}{}{\vspace{0pt}
}}
\begin{itemize}
\item {Validated a novel design of the blade-disc attachment in a gas turbine.}
\item {Studied the effects of the contact geometry, thermal stress, and manufacturing tolerances on the life cycle of the turbine rotor.}
% \item{Broaden the insight into the gas turbine, including the developing history of various products and their applications in industries}
\end{itemize}
\item \textbf{Research Areas:}\\
Finite element modeling and simulation, fatigue and topology optimization.
\end{itemize}

\section{Education}
\vspace{5pt}
%\subsection{Academic Qualifications}

\begin{itemize}
\item{\cventry{Sep 2016--Oct 2018}{M.S. in Solid Mechanics}{KTH Royal Institute of Technology, School of Engineering Mechanics}{Stockholm}{}{}}
\vspace{6pt}
\item{\cventry{Sep 2012--Aug 2016}{B.S. in Engineering Mechanics}{Beijing Institute of Technology, School of Mechatronical Engineering}{Beijing}{}{}}  % arguments 3 to 6 can be left empty
\end{itemize}

\section{Skills}
\begin{itemize}
\item \textbf{Programming Languages \& Frameworks:} \\
Proficient in Python ecosystem: OpenCV, Pandas, Scikit-learn, Scipy, FastAPI, Plotly, Dash. \\
Familiar with SQL, R, SAS, MATLAB, LaTeX, React, Docker, Azure DevOps.\\

\item \textbf{Cloud \& Infrastructure:} \\
Azure Synapse Analytics, Azure Machine Learning, Azure Web Apps, Azure Blob Storage, Azure Pipeline.\\

\item \textbf{AI \& Machine Learning:} \\
Prompt Engineering, RAG (Retrieval-Augmented Generation), LangChain, GPT-4, Gemini, AutoGen, Computer Vision Algorithms, Image Processing.\\

\item \textbf{Data Analytics \& Visualization:} \\
PowerBI, Data Warehousing, GPS Data Processing, Business Analytics, Financial Analytics, Patent Analytics.\\

\item \textbf{Languages:} \\
Native in Chinese. Fluent in English.
\end{itemize}

\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}           
\end{document} 